---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```

```{css}
body {
  background-color: #e8f5e9;
  font-family: Arial, sans-serif;
  margin: 20px;
}

h1 {
  color: #1b5e20;
}

h2 {
  color: #2e7d32;
}

p {
  font-size: 16px;
  line-height: 1.6;
}
```

## Introduction

This report documents my observations of bus passengers over several consecutive days, with a focus on whether they were wearing headphones. The data was collected through a Google form, and I recorded the results of each observation during the ride. In addition to headphone use, I also recorded the passengers' activities, the duration they spent on the bus, and the specific time of the ride.

The purpose of this data collection was to explore the behaviors of people in the daily public transportation environment. Through the analysis of this dataset, I learned about the widespread use of headphones among passengers and the other activities associated with it. The data is presented in a dynamic report format and is automatically updated as new data is added.

## Bus Passenger Headphone Usage

```{r}
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))

logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vQO9Qyksn-4DfN26YpXyWU9sMD85FLfrzqN719NOhOG--6z0lEIFXDW2Hn6nBK9C1Tm872wGr99_BQk/pub?output=csv"
)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    headphones = `Is the passenger wearing headphones?`,
    activity = `What is the passenger doing?`,
    minutes = `How many minutes have they been on the bus (estimated)?`,
    time_of_day = `Time of day`
  )
```

```{r results='asis', comment=NA}
prop_headphones <- round(mean(latest_data$headphones == "Yes") * 100, 1)
mean_minutes <- round(mean(latest_data$minutes), 1)

cat(paste0("Approximately ", prop_headphones,
           "% of observed passengers were wearing headphones.\n\n"))

cat(paste0("On average, observed passengers had been on the bus for ",
           mean_minutes, " minutes.\n\n"))
```

```{r}
ggplot(latest_data, aes(x = headphones)) +
  geom_bar() +
  labs(
    title = "Headphone use among observed bus passengers",
    x = "Wearing headphones",
    y = "Count"
  )
```

```{r}
ggplot(latest_data, aes(x = activity)) +
  geom_bar() +
  labs(
    title = "Activities of observed bus passengers",
    x = "Passenger activity",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
